### 2017-10-10 Gruba/06-perf.tex

>>>>

\stitle{Case Study for Feature Extraction}
In this section, we show the results of our demo system for user features extraction.
Considering the huge amount of users, we carefully selected one typical user for analysis.
Here we chose Mary(a famous drama and movie actor in China) as a representative.
The features extraction result for Mary is displayed in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(演员马丽) and she is from Beijing(北京). 
The number of followers of Mary is much more than the number of her friends.
The Sina Microblog tag she made for herself is "actor"(演员).
As the result of the long-term interest extraction shows, she is interested in stage performances(舞台喝彩), drama performances(话剧表演),films(电影光影) and so on, which is consistent with her actual situation.
What's more, the probability distribution of tweeting and retweeting behavior on different time periods in one day indicates that her activities at night is much more than daytime.
The time interval distribution of her behaviors is also shown in Fig.\ \ref{fig:userFeatures}. The time interval is mostly distributed within 48 hours, which indicates that she is a active user.
We developed a function for querying user's short-term interest. 
Here we queried Mary's short-term interest between 09/01/2016 and 09/30/2016, and got it as shown in Fig.\ \ref{fig:userFeatures}. We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(基督山伯爵). So the results are in line with expectations.

\begin{figure}
  \centering
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure{
  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure{
  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
\end{figure}
